%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Postgraduate Course - Mobile apps Development (Computer Science)} % Degree
    {PUCPR (Pontifical university Catholic of Parana)} % Institution
    {Curitiba, Brazil} % Location
    {Jan. 2016 - Mar. 2018 (Not finished)} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
\item {The Majoring Diploma in App Development offers an advanced curriculum in the development of solutions for mobile devices, interrelating methodologies and market technologies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bachelor of Technology in System Analysis and Development (Computer Science)} % Degree
    {UNOPAR (Universidade Norte do Paraná)} % Institution
    {Londrina, Brazil} % Location
    {Jan. 2013 - Dec. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
          \item {  This course I had the opportunity to study with a scholarship. }
\item {Basic training area of this course aims to integrate the student in the computer field, from the perspective of its object and give the theoretical and practical reasoning for that he can interpret and follow the disciplines of professional area, pointing for relations of Information Technology with the other disciplines.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Certificate Program in Software Development and Programming} % Degree
    {Instituto Senai} % Institution
    {Londrina, Brazil} % Location
    {Jan. 2012 - Dec. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
    \item {  This course I had the opportunity to study with a scholarship. }
\item {The objective of this course was form a professional who will apply the database concepts and will use the key technologies related to Java and Delphi platform for developing systems.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
