%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    { Software Engineer (DevOps/IOT)} % Job title
    {Rumo S.A} % Organization
    {Curitiba, Brazil} % Location
    {Oct. 2017 - PRESENT} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
Responsible for the development of real-time communication systems between equipments used by the RUMO trains and Internet (IOT) for data processing such as BI, monitoring, alarms, Machine Learning and etc.
}
       \item {In this opportunity I worked using the maximum of AWS Stack (EC2, DynamoDB, IOT, S3, Lambda, MQTT, SQS, SNS, Kinesis) for data processing and the Big Data stack (HDFS Hadoop, Cloudera, Impala, Hive, Oracle Analytics Cloud) for our Analytics system. In addition to using the most of the open-source technologies such as Python, Node.Js, Javascript (ES6), Java (Spring), AngularJS/5 and others.}
        \item {The initial focus of this role was to work in a project for the initiation and improvement of the devices/sensors used in the route by the RUMO's trains. Project which now have an average of 5 million rules executing in the AWS IOT daily for sending data to systems such as PRTG (monitoring) and Oracle Analytics Cloud (BigData) and PowerBI.}
          \item {In addition to IOT and Big Data projects, I had the opportunity to participate in the implementation of the DevOps methodology in Rumo with the automation of deploys of SOA, OS and Web projects and an automated Jira tracking. I also was able to help on the migration of VCS system from the Subversion to GIT (Bitbucket) and documentation with Confluence of projects.}
        \item {In the Rumo technology area we used the best of agile methodologies, using Scrum and Kanban and tools like Bitbucket (GIT) for project and code version management (VCS) and Jira and Confluence for documentation and issues.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Full Stack Software Engineer (Web - Mobile)} % Job title
    {Mirum Agency} % Organization
    {Curitiba, Brazil} % Location
    {Apr. 2016 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and maintenance of Mobile and Web applications using JS, IONIC, AngularJS, Cordova, Node.js, Adobe AEM, PHP, CodeIgniter, Drupal, MySQL and other technologies.}
        \item {In this opportunity I worked developing web apps for big clients on the world. One of our biggest clients was the Activia Danone websites (Drupal 8 websites), The West Ham United team website (Drupal 8) and the Ebook App for the Learning Factory company (Adobe AEM and IONIC) }
\item {In the IT area of Mirum we used agile methodologies, using Scrum and Kanban and tools like Bitbucket, Gitlab, Github (GIT) for project and code version management (VCS) and Jira and Confluence for documentation and issues.}
\end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer (GIS - WEB)} % Job title
    {Veltec} % Organization
    {Londrina, Brazil} % Location
    {Jul. 2015 - Mar. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { I this opportunity I worked as a Full Stack developer using technologies such Ruby on Rails, Node.js, PostgreSQL, ExtJS, Python, ShellScript, Georeferencing, Java, AngularJS and others}
\item {My main goal in the company was to be responsible for migrating the company's Georeferencing System (first development in Delphi and .shp files) to a microservice architecture taking full advantage of open source technologies like Ruby on Rails, Postgresql, Postgis, Python, OpenStreetMap, Java, Shellscript, AngularJs, EXTJS, D3.js, OpenLayers, Leaflet and others.}
\item {In the area of technology of Veltec we used agile methodologies using Scrum (daily meeting, Pair Progamming, Code Review and etc) and tools like Bitbucket (GIT) for project and code version management (VCS) and Redmine and Confluence for documentation and issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Software Engineer} % Job title
    {Z3 WEB Digital Agency} % Organization
    {Londrina, Brazil} % Location
    {Jan. 2015 - Jul. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Development and maintenance of websites using technologies such as Html5, PHP, Css, CakePHP, Javascript, Wordpress, Jquery, MySQL, among others.}
\item {In the Z3 Web technology area we used tools like Bitbucket (Git) for project and code version management (VCS) and RunRunIt for task management.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Support - Intern} % Job title
    {Amcor} % Organization
    {Cambé, Brazil} % Location
    {Jan. 2013 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical support for Windows and Linux systems, Lotus Notes and ERP System - Progress, backup systems and etc.}
        \item {Support for the Head Office in Brazil and offices in São Paulo.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

